# packages

```{r}
library(readxl)
library(sandwich)
library(car)
library(carData)
library(sp)
library(emmeans)
library(Matrix)
library(lme4)
library(DHARMa)
library(nlme)
library(glmmTMB)
library(ggplot2)
library(gstat)
library(ggpattern)
library(ggpubr)
library(ggthemes)
library(ggnewscale)
library(ggsignif)
library(multcomp)
library(multcompView)
library(emmeans)
library(AER)
library(MASS)
library(jtools)
library(interactions)
library(performance)
library(see)
library(nlme)
library(sjPlot)
library(tidyverse)
library(broom.mixed)
library(dplyr)
library(vegan)
library(survival)
library(survminer)
```

# data in

```{r}
all <- read_excel("C:/Master.xlsx", 
    na = "na")
#View(all)
```


# subsets
```{r}
all_pairs <- subset (all, sex == "f" & pair_ID != "na")
all_f <- subset (all, sex == "f")
all_m <- subset (all, sex == "m")
all_dev <- subset (all, a == "1")
```



#reorder levels and define data type
```{r}
all <- all %>%
  mutate(treatment = factor(treatment, levels = c("C", "A", "I", "M")))

all_f <- all_f %>%
  mutate(treatment = factor(treatment, levels = c("C", "A", "I", "M")))

all_m <- all_m %>%
  mutate(treatment = factor(treatment, levels = c("C", "A", "I", "M")))

all_pairs <- all_pairs %>%
  mutate(treatment = factor(treatment, levels = c("C", "A", "I", "M")))
```



# font

```{r}
windowsFonts(A = windowsFont("Arial"))
windowsFonts(B = windowsFont("Time News Roman"))
```



#boxplots and scatterplots


##Fig. 2A_F0 DEVELOPMENTAL TIME MF

```{r}

# Clean your data
all_clean <- all %>% drop_na(devtime_adult)


# Create base plot
devtime_adult_mf <- ggplot(all_clean, aes(x = treatment, y = devtime_adult)) +
  stat_boxplot(geom ="errorbar", width = 0.2) +
  geom_boxplot_pattern(
    outlier.shape = NA,
    aes(fill = treatment, pattern = treatment_format, pattern_colour = treatment_format),
    pattern_density = 0.45,
    pattern = c("none", "none", "none", "stripe")

  ) +
  scale_pattern_colour_manual(values = c("none" = NA, "stripe" = "#56C0BC")) +
  scale_pattern_manual(
    name = "Treatment",
    values = c("C" = "none", "A" = "none", "I" = "none", "M" = "stripe"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
  scale_fill_manual(
    name = "Treatment",
    values = c("C" = "#555352", "A" = "#FFD045", "I" = "#56C0BC", "M" = "#FFD045", "f" = "black", "m" = "black", "n" = "gray"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
 geom_jitter(aes(shape = sex_plots, fill = sex_plots), width = 0.3, height = 0.00, size = 3, color = "white") +
scale_shape_manual(
  name = "Sex",
  values = c("f" = 22, "m" = 21, "n" = 24),
  labels = c("f" = "female", "m" = "male", "n" = "unknown"))+
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 4,
    size = 3,
    color = "#8F8F8F",
    stroke = 2
  ) +  # mean above
  theme_classic(base_size = 10) +
  labs(x = element_blank(), y = "Developmental time [days]") +
  scale_x_discrete(labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix"))+
  theme(
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 20),
    text = element_text(family = "A")
  )


# Show the plot
devtime_adult_mf

# Save the plot
filename <- "devtime_adult_mf.svg"
ggsave(filename, plot = devtime_adult_mf, device = "svg", width = 6, height = 4)

cat("Plot saved as", filename, "in the working directory.\n")

```
```{r}
# Clean your data
all_clean <- all %>% drop_na(devtime_adult)


# --- Plot ---
devtime_adult_mf <- ggplot(all_clean, aes(x = treatment, y = devtime_adult)) +
  stat_boxplot(geom ="errorbar", width = 0.2) +
  geom_boxplot_pattern(
    outlier.shape = NA,
    aes(fill = treatment, pattern = treatment_format, pattern_colour = treatment_format),
    pattern_density = 0.45,
    pattern = c("none", "none", "none", "stripe")
  ) +
  scale_pattern_colour_manual(values = c("none" = NA, "stripe" = "#56C0BC")) +
  scale_pattern_manual(
    name = "Treatment",
    values = c("C" = "none", "A" = "none", "I" = "none", "M" = "stripe"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
  scale_fill_manual(
    name = "Treatment",
    values = c("C" = "#555352", "A" = "#FFD045", "I" = "#56C0BC", "M" = "#FFD045", 
               "f" = "black", "m" = "black", "n" = "gray"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
  geom_jitter(aes(shape = sex_plots, fill = sex_plots), 
              width = 0.3, height = 0.00, size = 2, color = "white") +
  scale_shape_manual(
    name = "Sex",
    values = c("f" = 22, "m" = 21, "n" = 24),
    labels = c("f" = "female", "m" = "male", "n" = "unknown")) +
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 4,
    size = 3,
    color = "#8F8F8F",
    stroke = 2
  ) +
  theme_classic(base_size = 10) +
  labs(x = element_blank(), y = "Developmental time [d]") +
  scale_x_discrete(labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")) +
  theme(
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 20),
    text = element_text(family = "A")
  )


# Show the plot
devtime_adult_mf

# Save the plot
filename <- "devtime_adult_mf.svg"
ggsave(filename, plot = devtime_adult_mf, device = "svg", width = 6, height = 4)

cat("Plot saved as", filename, "in the working directory.\n")

```

##Fig. 2B_F0 ADULT MASS MALE

```{r}
# Clean your data
all_m_clean <- all_m %>% drop_na(mass_a)


# Create base plot
mass_a_m <- ggplot(all_m_clean, aes(x = treatment, y = mass_a)) +
  stat_boxplot(geom ="errorbar", width = 0.2) +
  geom_boxplot_pattern(
    outlier.shape = NA,
    aes(fill = treatment, pattern = treatment_format, pattern_colour = treatment_format),
    pattern_density = 0.45,
    pattern = c("none", "none", "none", "stripe")

  ) +
  scale_pattern_colour_manual(values = c("none" = NA, "stripe" = "#56C0BC")) +
  scale_pattern_manual(
    name = "Treatment",
    values = c("C" = "none", "A" = "none", "I" = "none", "M" = "stripe"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
  scale_fill_manual(
    name = "Treatment",
    values = c("C" = "#555352", "A" = "#FFD045", "I" = "#56C0BC", "M" = "#FFD045", "f" = "black", "m" = "black", "n" = "gray"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
 geom_jitter(aes(shape = sex_plots, fill = sex_plots), width = 0.3, height = 0.00, size = 2, color = "white") +
scale_shape_manual(
  name = "Sex",
  values = c("f" = 22, "m" = 21, "n" = 24),
  labels = c("f" = "female", "m" = "male", "n" = "unknown"))+
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 4,
    size = 3,
    color = "#8F8F8F",
    stroke = 2
  ) +  # mean above
  theme_classic(base_size = 10) +
  labs(x = element_blank(), y = "Male adult mass [mg]") +
  scale_x_discrete(labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix"))+
  theme(
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 20),
    text = element_text(family = "A")
  )+
  ylim(4.5, 10.5)


# Show the plot
mass_a_m

# Save the plot
filename <- "mass_a_m.svg"
ggsave(filename, plot = mass_a_m, device = "svg", width = 6, height = 4)

cat("Plot saved as", filename, "in the working directory.\n")

```
##Fig. 2C_F0 ADULT MASS FEMALE

```{r}

# Clean your data
all_f_clean <- all_f %>% drop_na(mass_a)

# Fit model
f1 <- glmmTMB(mass_a ~ ALAN*Cooper, 
                    family = gaussian, 
                    data = all_f_clean, 
                    na.action = na.omit, REML = FALSE)

# Estimated marginal means and pairwise comparisons (Holm)
em <- emmeans(f1, pairwise ~ ALAN*Cooper, adjust = "holm")

# CLD
cld_letters <- cld(em$emmeans, Letters = letters, adjust = "holm") %>%
  as.data.frame() %>%
  rename(Letters = .group) %>%
  mutate(
    treatment = case_when(
      ALAN == 0 & Cooper == 0 ~ "C",
      ALAN == 1 & Cooper == 0 ~ "A",
      ALAN == 0 & Cooper == 1 ~ "I",
      ALAN == 1 & Cooper == 1 ~ "M"
    )
  )

# Remove whitespace
cld_letters$Letters <- trimws(cld_letters$Letters)


# Get max mass for y-positioning
max_vals <- all_f_clean %>%
  group_by(treatment) %>%
  summarise(max_mass = max(mass_a), .groups = "drop")

# Merge letter labels and max values
cld_letters <- left_join(cld_letters, max_vals, by = "treatment")

# Create base plot
mass_a_f <- ggplot(all_f_clean, aes(x = treatment, y = mass_a)) +
  stat_boxplot(geom ="errorbar", width = 0.2) +
  geom_boxplot_pattern(
    outlier.shape = NA,
    aes(fill = treatment, pattern = treatment_format, pattern_colour = treatment_format),
    pattern_density = 0.45,
    pattern = c("none", "none", "none", "stripe")

  ) +
  scale_pattern_colour_manual(values = c("none" = NA, "stripe" = "#56C0BC")) +
  scale_pattern_manual(
    name = "Treatment",
    values = c("C" = "none", "A" = "none", "I" = "none", "M" = "stripe"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
  scale_fill_manual(
    name = "Treatment",
    values = c("C" = "#555352", "A" = "#FFD045", "I" = "#56C0BC", "M" = "#FFD045", "f" = "black", "m" = "black", "n" = "gray"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
 geom_jitter(aes(shape = sex_plots, fill = sex_plots), width = 0.3, height = 0.00, size = 2, color = "white") +
scale_shape_manual(
  name = "Sex",
  values = c("f" = 22, "m" = 21, "n" = 24),
  labels = c("f" = "female", "m" = "male", "n" = "unknown"))+
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 4,
    size = 3,
    color = "#8F8F8F",
    stroke = 2
  ) +  # mean above
  theme_classic(base_size = 10) +
  labs(x = element_blank(), y = "Female adult mass [mg]") +
  scale_x_discrete(labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix"))+
  theme(
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 20),
    text = element_text(family = "A")
  )+
  ylim(4.5, 10.5)

# Add CLD letters or "n.s." depending on significance
if (length(unique(cld_letters$Letters)) == 1) {
  # All treatments have the same letter → no significant difference
  center_x <- mean(range(as.numeric(factor(cld_letters$treatment))))
  max_y <- max(cld_letters$max_mass) + 0.05 * max(all_f_clean$mass_a)
  
  mass_a_f <- mass_a_f +
    annotate("text", x = center_x, y = max_y, label = "n.s.", size = 5)
  
} else {
  # Show CLD letters per treatment
  mass_a_f <- mass_a_f +
    geom_text(data = cld_letters,
              aes(x = treatment, y = max_mass + 0.05 * max(all_f_clean$mass_a), label = Letters),
              inherit.aes = FALSE,
              size = 5)
}

# Show the plot
mass_a_f

# Save the plot
filename <- "mass_a_f.svg"
ggsave(filename, plot = mass_a_f, device = "svg", width = 6, height = 4)

cat("Plot saved as", filename, "in the working directory.\n")

```

##Fig. 2D_KAPLAN-MEIER SURVIVAL

```{r}
(survival <- Surv(all$time_days, all$status==1, type="right"))
#(survivalpre <- Surv(survpre$Time_days, survpre$Status==1, type="right"))
```

```{r}
surv_curve <- survfit(Surv(time_days, status==1)~treatment, data=all, type='kaplan-meier')

```

```{r}
# Extract data from survfit()
surv_df <- surv_summary(surv_curve, data = all)

# split data in groups
surv_C <- surv_df %>% filter(strata == "treatment=C")
surv_A <- surv_df %>% filter(strata == "treatment=A")
surv_I <- surv_df %>% filter(strata == "treatment=I")
surv_M <- surv_df %>% filter(strata == "treatment=M")

# extract censoring per group
censor_C <- surv_C %>% filter(!is.na(n.censor) & n.censor > 0)
censor_A <- surv_A %>% filter(!is.na(n.censor) & n.censor > 0)
censor_I <- surv_I %>% filter(!is.na(n.censor) & n.censor > 0)
censor_M <- surv_M %>% filter(!is.na(n.censor) & n.censor > 0)

# base plot
p <- ggplot() +
  # group C 
  geom_step(data = surv_C, aes(x = time, y = surv), color = "#555352", linetype = "solid", size = 1.1) +
  
  # group A 
  geom_step(data = surv_A, aes(x = time, y = surv), color = "#FFD045", linetype = "solid", size = 1.1) +
  
  # group I 
  geom_step(data = surv_I, aes(x = time, y = surv), color = "#56C0BC", linetype = "solid", size = 1.1) +

  # group M 
  geom_step(data = surv_M, aes(x = time, y = surv), color = "#56C0BC", linetype = "solid", size = 1.1) +

  # group M 
  geom_step(data = surv_M, aes(x = time, y = surv), color = "#FFD045", linetype = "dashed", size = 1.1) +

  # censoring details
  geom_point(data = censor_C, aes(x = time, y = surv), shape = 1, size = 4, stroke = 1, color = "#555352") +
  geom_point(data = censor_A, aes(x = time, y = surv), shape = 1, size = 4, stroke = 1, color = "#FFD045") +
  geom_point(data = censor_I, aes(x = time, y = surv), shape = 1, size = 4, stroke = 1, color = "#56C0BC") +
  geom_point(data = censor_M, aes(x = time, y = surv), shape = 1, size = 4, stroke = 1, color = "#56C0BC") +

  # axes and layout
  labs(x = "Time [d]", y = "Survival prob. [rel.]") +
  scale_x_continuous(limits = c(0, 32)) +
  scale_y_continuous(limits = c(0.0, 1.0)) +
  theme_classic(base_size = 10) +
  theme(axis.text = element_text(size = 16),
        axis.title = element_text(size = 20),
        text = element_text(family = "A"))

# safe
ggsave("survival_plot_M_doubled_with_censorings.svg", plot = p, width = 6, height = 4, device = "svg")

# show
print(p)

```


##Fig. 3A_F0 CONSUMPTION PRE I. MALE

```{r}

# Clean your data
all_m_clean <- all_m %>% drop_na(sum_pre)

# Create base plot
sum_pre_m <- ggplot(all_m_clean, aes(x = treatment, y = sum_pre)) +
  stat_boxplot(geom ="errorbar", width = 0.2) +
  geom_boxplot_pattern(
    outlier.shape = NA,
    aes(fill = treatment, pattern = treatment_format, pattern_colour = treatment_format),
    pattern_density = 0.45,
    pattern = c("none", "none", "none", "stripe")

  ) +
  scale_pattern_colour_manual(values = c("none" = NA, "stripe" = "#56C0BC")) +
  scale_pattern_manual(
    name = "Treatment",
    values = c("C" = "none", "A" = "none", "I" = "none", "M" = "stripe"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
  scale_fill_manual(
    name = "Treatment",
    values = c("C" = "#555352", "A" = "#FFD045", "I" = "#56C0BC", "M" = "#FFD045", "f" = "black", "m" = "black", "n" = "gray"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
 geom_jitter(aes(shape = sex_plots, fill = sex_plots), width = 0.3, height = 0.00, size = 2, color = "white") +
scale_shape_manual(
  name = "Sex",
  values = c("f" = 22, "m" = 21, "n" = 24),
  labels = c("f" = "female", "m" = "male", "n" = "unknown"))+
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 4,
    size = 3,
    color = "#8F8F8F",
    stroke = 2
  ) +  # mean above
  theme_classic(base_size = 10) +
  labs(x = element_blank(), y = "Feeding amount [mm^2]") +
  scale_x_discrete(labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix"))+
  theme(
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 20),
    text = element_text(family = "A")
  )


# Show the plot
sum_pre_m

# Save the plot
filename <- "sum_pre_m.svg"
ggsave(filename, plot = sum_pre_m, device = "svg", width = 6, height = 4)

cat("Plot saved as", filename, "in the working directory.\n")

```


##Fig. 3B_F0 CONSUMPTION PRE I. FEMALE

```{r}

# Clean your data
all_f_clean <- all_f %>% drop_na(sum_pre)


# Create base plot
sum_pre_f <- ggplot(all_f_clean, aes(x = treatment, y = sum_pre)) +
  stat_boxplot(geom ="errorbar", width = 0.2) +
  geom_boxplot_pattern(
    outlier.shape = NA,
    aes(fill = treatment, pattern = treatment_format, pattern_colour = treatment_format),
    pattern_density = 0.45,
    pattern = c("none", "none", "none", "stripe")

  ) +
  scale_pattern_colour_manual(values = c("none" = NA, "stripe" = "#56C0BC")) +
  scale_pattern_manual(
    name = "Treatment",
    values = c("C" = "none", "A" = "none", "I" = "none", "M" = "stripe"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
  scale_fill_manual(
    name = "Treatment",
    values = c("C" = "#555352", "A" = "#FFD045", "I" = "#56C0BC", "M" = "#FFD045", "f" = "black", "m" = "black", "n" = "gray"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
 geom_jitter(aes(shape = sex_plots, fill = sex_plots), width = 0.3, height = 0.00, size = 2, color = "white") +
scale_shape_manual(
  name = "Sex",
  values = c("f" = 22, "m" = 21, "n" = 24),
  labels = c("f" = "female", "m" = "male", "n" = "unknown"))+
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 4,
    size = 3,
    color = "#8F8F8F",
    stroke = 2
  ) +  # mean above
  theme_classic(base_size = 10) +
  labs(x = element_blank(), y = "Feeding amount [mm^2]") +
  scale_x_discrete(labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix"))+
  theme(
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 20),
    text = element_text(family = "A")
  )+
  scale_y_continuous(
  breaks = seq(50, 200, 50),
  limits = c(0, 205),
  expand = expansion(mult = c(0, 0.05))
)


# Show the plot
sum_pre_f

# Save the plot
filename <- "sum_pre_f.svg"
ggsave(filename, plot = sum_pre_f, device = "svg", width = 6, height = 4)

cat("Plot saved as", filename, "in the working directory.\n")

```
```{r}
## ------------------------------
##  CLEAN DATA
## ------------------------------

all_f_clean <- all_f %>% drop_na(sum_pre)


## ------------------------------
##  PLOT: Feeding amount (mm²)
## ------------------------------

sum_pre_f <- ggplot(all_f_clean, aes(x = treatment, y = sum_pre)) +
  stat_boxplot(geom = "errorbar", width = 0.2) +
  
  # Boxplots with patterns
  geom_boxplot_pattern(
    outlier.shape = NA,
    aes(fill = treatment,
        pattern = treatment_format,
        pattern_colour = treatment_format),
    pattern_density = 0.45,
    pattern = c("none", "none", "none", "stripe")
  ) +
  
  # Patterns legend
  scale_pattern_colour_manual(values = c("none" = NA, "stripe" = "#56C0BC")) +
  scale_pattern_manual(
    name = "Treatment",
    values = c("C" = "none", "A" = "none", "I" = "none", "M" = "stripe"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
  
  # Colors legend
  scale_fill_manual(
    name = "Treatment",
    values = c("C" = "#555352",
               "A" = "#FFD045",
               "I" = "#56C0BC",
               "M" = "#FFD045",
               "f" = "black",
               "m" = "black",
               "n" = "gray"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
  
  # Jittered points (sex shapes)
  geom_jitter(aes(shape = sex_plots, fill = sex_plots),
              width = 0.3, height = 0, size = 2, color = "white") +
  scale_shape_manual(
    name = "Sex",
    values = c("f" = 22, "m" = 21, "n" = 24),
    labels = c("f" = "female", "m" = "male", "n" = "unknown")
  ) +
  
  # Mean marker (grey X)
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 4,
    size = 3,
    color = "#8F8F8F",
    stroke = 2
  ) +
  
  # Axis and labels
  theme_classic(base_size = 10) +
  labs(x = element_blank(), y = "Feeding amount [mm^2]") +
  scale_x_discrete(labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")) +
  
  # Standardize Y axis for comparability across plots
  scale_y_continuous(limits = c(0, 200),
                     breaks = seq(50, 200, 50)) +
  
  # Theme
  theme(
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 20),
    text = element_text(family = "A")
  )

# Show the plot
sum_pre_f

# Save the plot
filename <- "sum_pre_f.svg"
ggsave(filename, plot = sum_pre_f, device = "svg", width = 6, height = 4)

cat("Plot saved as", filename, "in the working directory.\n")

```



##Fig. 3C_F0 CONSUMPTION DURING I. MALE

```{r}

# Clean your data
all_m_clean <- all_m %>% drop_na(sum_per)


# Create base plot
sum_per_m <- ggplot(all_m_clean, aes(x = treatment, y = sum_per)) +
  stat_boxplot(geom ="errorbar", width = 0.2) +
  geom_boxplot_pattern(
    outlier.shape = NA,
    aes(fill = treatment, pattern = treatment_format, pattern_colour = treatment_format),
    pattern_density = 0.45,
    pattern = c("none", "none", "none", "stripe")

  ) +
  scale_pattern_colour_manual(values = c("none" = NA, "stripe" = "#56C0BC")) +
  scale_pattern_manual(
    name = "Treatment",
    values = c("C" = "none", "A" = "none", "I" = "none", "M" = "stripe"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
  scale_fill_manual(
    name = "Treatment",
    values = c("C" = "#555352", "A" = "#FFD045", "I" = "#56C0BC", "M" = "#FFD045", "f" = "black", "m" = "black", "n" = "gray"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
 geom_jitter(aes(shape = sex_plots, fill = sex_plots), width = 0.3, height = 0.00, size = 2, color = "white") +
scale_shape_manual(
  name = "Sex",
  values = c("f" = 22, "m" = 21, "n" = 24),
  labels = c("f" = "female", "m" = "male", "n" = "unknown"))+
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 4,
    size = 3,
    color = "#8F8F8F",
    stroke = 2
  ) +  # mean above
  theme_classic(base_size = 10) +
  labs(x = element_blank(), y = "Feeding amount [mm^2]") +
  scale_x_discrete(labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix"))+
  theme(
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 20),
    text = element_text(family = "A")
  )

# Show the plot
sum_per_m

# Save the plot
filename <- "sum_per_m.svg"
ggsave(filename, plot = sum_per_m, device = "svg", width = 6, height = 4)

cat("Plot saved as", filename, "in the working directory.\n")

```

##Fig. 3D_F0 CONSUMPTION DURING I. FEMALE

```{r}

# Clean your data
all_f_clean <- all_f %>% drop_na(sum_per)

# Merge letter labels and max values
cld_letters <- left_join(cld_letters, max_vals, by = "treatment")

# Create base plot
sum_per_f <- ggplot(all_f_clean, aes(x = treatment, y = sum_per)) +
  stat_boxplot(geom ="errorbar", width = 0.2) +
  geom_boxplot_pattern(
    outlier.shape = NA,
    aes(fill = treatment, pattern = treatment_format, pattern_colour = treatment_format),
    pattern_density = 0.45,
    pattern = c("none", "none", "none", "stripe")

  ) +
  scale_pattern_colour_manual(values = c("none" = NA, "stripe" = "#56C0BC")) +
  scale_pattern_manual(
    name = "Treatment",
    values = c("C" = "none", "A" = "none", "I" = "none", "M" = "stripe"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
  scale_fill_manual(
    name = "Treatment",
    values = c("C" = "#555352", "A" = "#FFD045", "I" = "#56C0BC", "M" = "#FFD045", "f" = "black", "m" = "black", "n" = "gray"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
 geom_jitter(aes(shape = sex_plots, fill = sex_plots), width = 0.3, height = 0.00, size = 2, color = "white") +
scale_shape_manual(
  name = "Sex",
  values = c("f" = 22, "m" = 21, "n" = 24),
  labels = c("f" = "female", "m" = "male", "n" = "unknown"))+
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 4,
    size = 3,
    color = "#8F8F8F",
    stroke = 2
  ) +  # mean above
  theme_classic(base_size = 10) +
  labs(x = element_blank(), y = "Feeding amount [mm^2]") +
  scale_x_discrete(labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix"))+
  theme(
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 20),
    text = element_text(family = "A")
  )

# Show the plot
sum_per_f

# Save the plot
filename <- "sum_per_f.svg"
ggsave(filename, plot = sum_per_f, device = "svg", width = 6, height = 4)

cat("Plot saved as", filename, "in the working directory.\n")

```

##Fig. 3E_F0 CONSUMPTION POST I. MALE

```{r}

# Clean your data
all_m_clean <- all_m %>% drop_na(sum_post)

# Create base plot
sum_post_m <- ggplot(all_m_clean, aes(x = treatment, y = sum_post)) +
  stat_boxplot(geom ="errorbar", width = 0.2) +
  geom_boxplot_pattern(
    outlier.shape = NA,
    aes(fill = treatment, pattern = treatment_format, pattern_colour = treatment_format),
    pattern_density = 0.45,
    pattern = c("none", "none", "none", "stripe")

  ) +
  scale_pattern_colour_manual(values = c("none" = NA, "stripe" = "#56C0BC")) +
  scale_pattern_manual(
    name = "Treatment",
    values = c("C" = "none", "A" = "none", "I" = "none", "M" = "stripe"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
  scale_fill_manual(
    name = "Treatment",
    values = c("C" = "#555352", "A" = "#FFD045", "I" = "#56C0BC", "M" = "#FFD045", "f" = "black", "m" = "black", "n" = "gray"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
 geom_jitter(aes(shape = sex_plots, fill = sex_plots), width = 0.3, height = 0.00, size = 2, color = "white") +
scale_shape_manual(
  name = "Sex",
  values = c("f" = 22, "m" = 21, "n" = 24),
  labels = c("f" = "female", "m" = "male", "n" = "unknown"))+
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 4,
    size = 3,
    color = "#8F8F8F",
    stroke = 2
  ) +  # mean above
  theme_classic(base_size = 10) +
  labs(x = element_blank(), y = "Feeding amount [mm^2]") +
  scale_x_discrete(labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix"))+
  theme(
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 20),
    text = element_text(family = "A")
  )+
  ylim(0, 650)

# Show the plot
sum_post_m

# Save the plot
filename <- "sum_post_m.svg"
ggsave(filename, plot = sum_post_m, device = "svg", width = 6, height = 4)

cat("Plot saved as", filename, "in the working directory.\n")

```

##Fig. 3F_F0 CONSUMPTION POST I. FEMALE

```{r}

# Clean your data
all_f_clean <- all_f %>% drop_na(sum_post)

# Create base plot
sum_post_f <- ggplot(all_f_clean, aes(x = treatment, y = sum_post)) +
  stat_boxplot(geom ="errorbar", width = 0.2) +
  geom_boxplot_pattern(
    outlier.shape = NA,
    aes(fill = treatment, pattern = treatment_format, pattern_colour = treatment_format),
    pattern_density = 0.45,
    pattern = c("none", "none", "none", "stripe")

  ) +
  scale_pattern_colour_manual(values = c("none" = NA, "stripe" = "#56C0BC")) +
  scale_pattern_manual(
    name = "Treatment",
    values = c("C" = "none", "A" = "none", "I" = "none", "M" = "stripe"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
  scale_fill_manual(
    name = "Treatment",
    values = c("C" = "#555352", "A" = "#FFD045", "I" = "#56C0BC", "M" = "#FFD045", "f" = "black", "m" = "black", "n" = "gray"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
 geom_jitter(aes(shape = sex_plots, fill = sex_plots), width = 0.3, height = 0.00, size = 2, color = "white") +
scale_shape_manual(
  name = "Sex",
  values = c("f" = 22, "m" = 21, "n" = 24),
  labels = c("f" = "female", "m" = "male", "n" = "unknown"))+
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 4,
    size = 3,
    color = "#8F8F8F",
    stroke = 2
  ) +  # mean above
  theme_classic(base_size = 10) +
  labs(x = element_blank(), y = "Feeding amount [mm^2]") +
  scale_x_discrete(labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix"))+
  theme(
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 20),
    text = element_text(family = "A")
  )+
  ylim(0, 650)

# Show the plot
sum_post_f

# Save the plot
filename <- "sum_post_f.svg"
ggsave(filename, plot = sum_post_f, device = "svg", width = 6, height = 4)

cat("Plot saved as", filename, "in the working directory.\n")

```






##Fig. 4A_F0 MATING DELAY PAIRS

```{r}

# Clean your data
all_pairs_clean <- all_pairs %>% drop_na(min_until_mating)

# Create base plot
min_until_mating_mf <- ggplot(all_pairs_clean, aes(x = treatment, y = min_until_mating)) +
  stat_boxplot(geom ="errorbar", width = 0.2) +
  geom_boxplot_pattern(
    outlier.shape = NA,
    aes(fill = treatment, pattern = treatment_format, pattern_colour = treatment_format),
    pattern_density = 0.45,
    pattern = c("none", "none", "none", "stripe")

  ) +
  scale_pattern_colour_manual(values = c("none" = NA, "stripe" = "#56C0BC")) +
  scale_pattern_manual(
    name = "Treatment",
    values = c("C" = "none", "A" = "none", "I" = "none", "M" = "stripe"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
  scale_fill_manual(
    name = "Treatment",
    values = c("C" = "#555352", "A" = "#FFD045", "I" = "#56C0BC", "M" = "#FFD045", "f" = "black", "m" = "black", "n" = "gray"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
 geom_jitter(aes(shape = sex_plots, fill = sex_plots), width = 0.3, height = 0.00, size = 2, color = "white") +
scale_shape_manual(
  name = "Sex",
  values = c("f" = 24, "m" = 24, "n" = 20),
  labels = c("f" = "female", "m" = "male", "n" = "unknown"))+
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 4,
    size = 3,
    color = "#8F8F8F",
    stroke = 2
  ) +  # mean above
  theme_classic(base_size = 10) +
  labs(x = element_blank(), y = "Time until mating [min]") +
  scale_x_discrete(labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix"))+
  theme(
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 20),
    text = element_text(family = "A")
  )

# Show the plot
min_until_mating_mf

# Save the plot
filename <- "min_until_mating_mf.svg"
ggsave(filename, plot = min_until_mating_mf, device = "svg", width = 6, height = 4)

cat("Plot saved as", filename, "in the working directory.\n")

```

##Fig. 4B_F1 EGG  NO. 

```{r}

# Clean your data
all_pairs_clean <- all_pairs %>% drop_na(egg_no._corrected)

# Create base plot
egg_no._corrected_mf <- ggplot(all_pairs_clean, aes(x = treatment, y = egg_no._corrected)) +
  stat_boxplot(geom ="errorbar", width = 0.2) +
  geom_boxplot_pattern(
    outlier.shape = NA,
    aes(fill = treatment, pattern = treatment_format, pattern_colour = treatment_format),
    pattern_density = 0.45,
    pattern = c("none", "none", "none", "stripe")

  ) +
  scale_pattern_colour_manual(values = c("none" = NA, "stripe" = "#56C0BC")) +
  scale_pattern_manual(
    name = "Treatment",
    values = c("C" = "none", "A" = "none", "I" = "none", "M" = "stripe"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
  scale_fill_manual(
    name = "Treatment",
    values = c("C" = "#555352", "A" = "#FFD045", "I" = "#56C0BC", "M" = "#FFD045", "f" = "black", "m" = "black", "n" = "gray"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
 geom_jitter(aes(shape = sex_plots, fill = sex_plots), width = 0.3, height = 0.00, size = 2, color = "white") +
scale_shape_manual(
  name = "Sex",
  values = c("f" = 24, "m" = 24, "n" = 20),
  labels = c("f" = "female", "m" = "male", "n" = "unknown"))+
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 4,
    size = 3,
    color = "#8F8F8F",
    stroke = 2
  ) +  # mean above
  theme_classic(base_size = 10) +
  labs(x = element_blank(), y = "Egg number") +
  scale_x_discrete(labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix"))+
  theme(
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 20),
    text = element_text(family = "A")
  )


# Show the plot
egg_no._corrected_mf

# Save the plot
filename <- "egg_no._corrected_mf.svg"
ggsave(filename, plot = egg_no._corrected_mf, device = "svg", width = 6, height = 4)

cat("Plot saved as", filename, "in the working directory.\n")

```

##Fig. 4C_F1 HATCHING RATE
```{r}

# Clean your data
all_pairs_clean <- all_pairs %>% drop_na(hatching_rate)

# Create base plot
hatching_rate_mf <- ggplot(all_pairs_clean, aes(x = treatment, y = hatching_rate)) +
  stat_boxplot(geom ="errorbar", width = 0.2) +
  geom_boxplot_pattern(
    outlier.shape = NA,
    aes(fill = treatment, pattern = treatment_format, pattern_colour = treatment_format),
    pattern_density = 0.45,
    pattern = c("none", "none", "none", "stripe")

  ) +
  scale_pattern_colour_manual(values = c("none" = NA, "stripe" = "#56C0BC")) +
  scale_pattern_manual(
    name = "Treatment",
    values = c("C" = "none", "A" = "none", "I" = "none", "M" = "stripe"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
  scale_fill_manual(
    name = "Treatment",
    values = c("C" = "#555352", "A" = "#FFD045", "I" = "#56C0BC", "M" = "#FFD045", "f" = "black", "m" = "black", "n" = "gray"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
 geom_jitter(aes(shape = sex_plots, fill = sex_plots), width = 0.3, height = 0.00, size = 2, color = "white") +
scale_shape_manual(
  name = "Sex",
  values = c("f" = 24, "m" = 24, "n" = 20),
  labels = c("f" = "female", "m" = "male", "n" = "unknown"))+
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 4,
    size = 3,
    color = "#8F8F8F",
    stroke = 2
  ) +  # mean above
  theme_classic(base_size = 10) +
  labs(x = element_blank(), y = "Hatching rate [%]") +
  scale_x_discrete(labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix"))+
  theme(
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 20),
    text = element_text(family = "A")
  )


# Show the plot
hatching_rate_mf

# Save the plot
filename <- "hatching_rate_mf.svg"
ggsave(filename, plot = hatching_rate_mf, device = "svg", width = 6, height = 4)

cat("Plot saved as", filename, "in the working directory.\n")

```

##Fig. S1A_F0 LARVAL MASS MF

```{r}

# Clean your data
all_clean <- all %>% drop_na(mass_l)

# Fit model
model <- lm(mass_l ~ treatment, data = all_clean)

# Estimated marginal means and pairwise comparisons (Holm)
em <- emmeans(model, pairwise ~ treatment, adjust = "holm")

# Get Compact Letter Display with actual letters (not numbers!)
cld_letters <- cld(em$emmeans, Letters = letters, adjust = "holm") %>%
  as.data.frame() %>%
  rename(Letters = .group)

# Remove leading/trailing whitespace from letters (important!)
cld_letters$Letters <- trimws(cld_letters$Letters)

# Get max mass for y-positioning
max_vals <- all_clean %>%
  group_by(treatment) %>%
  summarise(max_mass = max(mass_l), .groups = "drop")

# Merge letter labels and max values
cld_letters <- left_join(cld_letters, max_vals, by = "treatment")

# Create base plot
massl_mf <- ggplot(all_clean, aes(x = treatment, y = mass_l)) +
  stat_boxplot(geom ="errorbar", width = 0.2) +
  geom_boxplot_pattern(
    outlier.shape = NA,
    aes(fill = treatment, pattern = treatment_format, pattern_colour = treatment_format),
    pattern_density = 0.45,
    pattern = c("none", "none", "none", "stripe")

  ) +
  scale_pattern_colour_manual(values = c("none" = NA, "stripe" = "#56C0BC")) +
  scale_pattern_manual(
    name = "Treatment",
    values = c("C" = "none", "A" = "none", "I" = "none", "M" = "stripe"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
  scale_fill_manual(
    name = "Treatment",
    values = c("C" = "#555352", "A" = "#FFD045", "I" = "#56C0BC", "M" = "#FFD045", "f" = "black", "m" = "black", "n" = "gray"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
 geom_jitter(aes(shape = sex_plots, fill = sex_plots), width = 0.3, height = 0.00, size = 2, color = "white") +
scale_shape_manual(
  name = "Sex",
  values = c("f" = 22, "m" = 21, "n" = 24),
  labels = c("f" = "female", "m" = "male", "n" = "unknown"))+
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 4,
    size = 3,
    color = "#8F8F8F",
    stroke = 2
  ) +  # mean above
  theme_classic(base_size = 10) +
  labs(x = element_blank(), y = "Larval mass [mg]") +
  scale_x_discrete(labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix"))+
  theme(
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 20),
    text = element_text(family = "A")
  )

# Add CLD letters or "n.s." depending on significance
if (length(unique(cld_letters$Letters)) == 1) {
  # All treatments have the same letter → no significant difference
  center_x <- mean(range(as.numeric(factor(cld_letters$treatment))))
  max_y <- max(cld_letters$max_mass) + 0.05 * max(all_clean$mass_l)
  
  massl_mf <- massl_mf +
    annotate("text", x = center_x, y = max_y, label = "n.s.", size = 5)
  
} else {
  # Show CLD letters per treatment
  massl_mf <- massl_mf +
    geom_text(data = cld_letters,
              aes(x = treatment, y = max_mass + 0.05 * max(all_clean$mass_l), label = Letters),
              inherit.aes = FALSE,
              size = 5)
}

# Show the plot
massl_mf

# Save the plot
filename <- "massl_mf.svg"
ggsave(filename, plot = massl_mf, device = "svg", width = 6, height = 4)

cat("Plot saved as", filename, "in the working directory.\n")

```



##Fig. S1B_F0 DELTA PUPAL-LARVAL MASS MALE

```{r}

# Clean your data
all_m_clean <- all_m %>% drop_na(delta_lp)

# Create base plot
delta_lp_m <- ggplot(all_m_clean, aes(x = treatment, y = delta_lp)) +
  stat_boxplot(geom ="errorbar", width = 0.2) +
  geom_boxplot_pattern(
    outlier.shape = NA,
    aes(fill = treatment, pattern = treatment_format, pattern_colour = treatment_format),
    pattern_density = 0.45,
    pattern = c("none", "none", "none", "stripe")

  ) +
  scale_pattern_colour_manual(values = c("none" = NA, "stripe" = "#56C0BC")) +
  scale_pattern_manual(
    name = "Treatment",
    values = c("C" = "none", "A" = "none", "I" = "none", "M" = "stripe"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
  scale_fill_manual(
    name = "Treatment",
    values = c("C" = "#555352", "A" = "#FFD045", "I" = "#56C0BC", "M" = "#FFD045", "f" = "black", "m" = "black", "n" = "gray"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
 geom_jitter(aes(shape = sex_plots, fill = sex_plots), width = 0.3, height = 0.00, size = 2, color = "white") +
scale_shape_manual(
  name = "Sex",
  values = c("f" = 22, "m" = 21, "n" = 24),
  labels = c("f" = "female", "m" = "male", "n" = "unknown"))+
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 4,
    size = 3,
    color = "#8F8F8F",
    stroke = 2
  ) +  # mean above
  theme_classic(base_size = 10) +
  labs(x = element_blank(), y = "Male delta pupal-larval mass [mg]") +
  scale_x_discrete(labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix"))+
  theme(
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 20),
    text = element_text(family = "A")
  )+
  ylim(4.5, 9.5)


# Show the plot
delta_lp_m

# Save the plot
filename <- "delta_lp_m.svg"
ggsave(filename, plot = delta_lp_m, device = "svg", width = 6, height = 4)

cat("Plot saved as", filename, "in the working directory.\n")

```

##Fig. S1C_F0 DELTA PUPAL-LARVAL MASS FEMALE

```{r}

# Clean your data
all_f_clean <- all_f %>% drop_na(delta_lp)

# Create base plot
delta_lp_f <- ggplot(all_f_clean, aes(x = treatment, y = delta_lp)) +
  stat_boxplot(geom ="errorbar", width = 0.2) +
  geom_boxplot_pattern(
    outlier.shape = NA,
    aes(fill = treatment, pattern = treatment_format, pattern_colour = treatment_format),
    pattern_density = 0.45,
    pattern = c("none", "none", "none", "stripe")

  ) +
  scale_pattern_colour_manual(values = c("none" = NA, "stripe" = "#56C0BC")) +
  scale_pattern_manual(
    name = "Treatment",
    values = c("C" = "none", "A" = "none", "I" = "none", "M" = "stripe"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
  scale_fill_manual(
    name = "Treatment",
    values = c("C" = "#555352", "A" = "#FFD045", "I" = "#56C0BC", "M" = "#FFD045", "f" = "black", "m" = "black", "n" = "gray"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
 geom_jitter(aes(shape = sex_plots, fill = sex_plots), width = 0.3, height = 0.00, size = 2, color = "white") +
scale_shape_manual(
  name = "Sex",
  values = c("f" = 22, "m" = 21, "n" = 24),
  labels = c("f" = "female", "m" = "male", "n" = "unknown"))+
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 4,
    size = 3,
    color = "#8F8F8F",
    stroke = 2
  ) +  # mean above
  theme_classic(base_size = 10) +
  labs(x = element_blank(), y = "Female delta pupal-larval mass [mg]") +
  scale_x_discrete(labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix"))+
  theme(
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 20),
    text = element_text(family = "A")
  )+
  ylim(4.5, 9.5)


# Show the plot
delta_lp_f

# Save the plot
filename <- "delta_lp_f.svg"
ggsave(filename, plot = delta_lp_f, device = "svg", width = 6, height = 4)

cat("Plot saved as", filename, "in the working directory.\n")

```
##Fig. S1D_F0 DELTA PUPAL-LARVAL MASS x TOTAL CONSUMPTION MALE

```{r}
# Prepare data
all_m_clean <- all_m %>%
  mutate(
    treatment = case_when(
      ALAN == 0 & Cooper == 0 ~ "C",
      ALAN == 1 & Cooper == 0 ~ "A",
      ALAN == 0 & Cooper == 1 ~ "I",
      ALAN == 1 & Cooper == 1 ~ "M",
      TRUE ~ NA_character_
    ),
    treatment = factor(treatment, levels = c("C", "A", "I", "M"))
  ) %>%
  filter(!is.na(food_total), !is.na(delta_lp), is.finite(food_total), delta_lp > 0)

# Plot
resultam <- ggplot(all_m_clean, aes(x = food_total, y = log(delta_lp),
                        color = treatment, linetype = treatment)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(method = "lm", se = FALSE, linewidth = 1.2) +
  scale_color_manual(
    name = "Treatment",
    values = c(
      "C" = "#555352",  # Control (gray)
      "A" = "#FFD045",  # ALAN (yellow)
      "I" = "#56C0BC",  # Insecticide (blue)
      "M" = "red"   # Mix (yellow)
    ),
    labels = c("C" = "Control", "A" = "ALAN",
               "I" = "Insecticide", "M" = "Mix")
  ) +
  scale_linetype_manual(
    name = "Treatment",
    values = c(
      "C" = "solid",
      "A" = "solid",
      "I" = "solid",
      "M" = "dashed"
    ),
    labels = c("C" = "Control", "A" = "ALAN",
               "I" = "Insecticide", "M" = "Mix")
  ) +
  labs(
    x = "Total feeding amount [mm^2]",
    y = "Delta mass [mg]"
  ) +
  theme_classic(base_size = 10) +
  theme(
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 20),
    plot.title = element_text(size = 22, hjust = 0.5),
    legend.title = element_text(size = 16),
    legend.text = element_text(size = 14),
    text = element_text(family = "A")
  ) +
xlim(500, 1000)+
  ylim(1.6, 2.2)

resultam

# Save the plot
filename <- "resultam.svg"
ggsave(filename, plot = resultam, device = "svg", width = 6, height = 4)

cat("Plot saved as", filename, "in the working directory.\n")

```


##Fig. S1E_F0 DELTA PUPAL-LARVAL MASS x TOTAL CONSUMPTION FEMALE

```{r}
# Prepare data
all_f_clean <- all_f %>%
  mutate(
    treatment = case_when(
      ALAN == 0 & Cooper == 0 ~ "C",
      ALAN == 1 & Cooper == 0 ~ "A",
      ALAN == 0 & Cooper == 1 ~ "I",
      ALAN == 1 & Cooper == 1 ~ "M",
      TRUE ~ NA_character_
    ),
    treatment = factor(treatment, levels = c("C", "A", "I", "M"))
  ) %>%
  filter(!is.na(food_total), !is.na(delta_lp), is.finite(food_total), delta_lp > 0)

# Plot
resulta <- ggplot(all_f_clean, aes(x = food_total, y = log(delta_lp),
                        color = treatment, linetype = treatment)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(method = "lm", se = FALSE, linewidth = 1.2) +
  scale_color_manual(
    name = "Treatment",
    values = c(
      "C" = "#555352",  # Control (gray)
      "A" = "#FFD045",  # ALAN (yellow)
      "I" = "#56C0BC",  # Insecticide (blue)
      "M" = "red"   # Mix (yellow)
    ),
    labels = c("C" = "Control", "A" = "ALAN",
               "I" = "Insecticide", "M" = "Mix")
  ) +
  scale_linetype_manual(
    name = "Treatment",
    values = c(
      "C" = "solid",
      "A" = "solid",
      "I" = "solid",
      "M" = "dashed"
    ),
    labels = c("C" = "Control", "A" = "ALAN",
               "I" = "Insecticide", "M" = "Mix")
  ) +
  labs(
    x = "Total feeding amount [mm^2]",
    y = "Delta mass [mg]"
  ) +
  theme_classic(base_size = 10) +
  theme(
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 20),
    plot.title = element_text(size = 22, hjust = 0.5),
    legend.title = element_text(size = 16),
    legend.text = element_text(size = 14),
    text = element_text(family = "A")
  )+
  xlim(500, 1000)+
  ylim(1.6, 2.2)

resulta

# Save the plot
filename <- "resulta.svg"
ggsave(filename, plot = resulta, device = "svg", width = 6, height = 4)

cat("Plot saved as", filename, "in the working directory.\n")

```

##Fig. S2A_F0 TOTAL CONSUMPTION MALE

```{r}

# Clean your data
all_m_clean <- all_m %>% drop_na(food_total)


# Create base plot
food_total_m <- ggplot(all_m_clean, aes(x = treatment, y = food_total)) +
  stat_boxplot(geom ="errorbar", width = 0.2) +
  geom_boxplot_pattern(
    outlier.shape = NA,
    aes(fill = treatment, pattern = treatment_format, pattern_colour = treatment_format),
    pattern_density = 0.45,
    pattern = c("none", "none", "none", "stripe")

  ) +
  scale_pattern_colour_manual(values = c("none" = NA, "stripe" = "#56C0BC")) +
  scale_pattern_manual(
    name = "Treatment",
    values = c("C" = "none", "A" = "none", "I" = "none", "M" = "stripe"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
  scale_fill_manual(
    name = "Treatment",
    values = c("C" = "#555352", "A" = "#FFD045", "I" = "#56C0BC", "M" = "#FFD045", "f" = "black", "m" = "black", "n" = "gray"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
 geom_jitter(aes(shape = sex_plots, fill = sex_plots), width = 0.3, height = 0.00, size = 2, color = "white") +
scale_shape_manual(
  name = "Sex",
  values = c("f" = 22, "m" = 21, "n" = 24),
  labels = c("f" = "female", "m" = "male", "n" = "unknown"))+
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 4,
    size = 3,
    color = "#8F8F8F",
    stroke = 2
  ) +  # mean above
  theme_classic(base_size = 10) +
  labs(x = element_blank(), y = "Male total consumption [mm^2]") +
  scale_x_discrete(labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix"))+
  theme(
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 20),
    text = element_text(family = "A")
  )+
  ylim(450, 1200)

# Show the plot
food_total_m

# Save the plot
filename <- "food_total_m.svg"
ggsave(filename, plot = food_total_m, device = "svg", width = 6, height = 4)

cat("Plot saved as", filename, "in the working directory.\n")

```

##Fig. S2B_F0 TOTAL CONSUMPTION FEMALE

```{r}

# Clean your data
all_f_clean <- all_f %>% drop_na(food_total)

# Create base plot
food_total_f <- ggplot(all_f_clean, aes(x = treatment, y = food_total)) +
  stat_boxplot(geom ="errorbar", width = 0.2) +
  geom_boxplot_pattern(
    outlier.shape = NA,
    aes(fill = treatment, pattern = treatment_format, pattern_colour = treatment_format),
    pattern_density = 0.45,
    pattern = c("none", "none", "none", "stripe")

  ) +
  scale_pattern_colour_manual(values = c("none" = NA, "stripe" = "#56C0BC")) +
  scale_pattern_manual(
    name = "Treatment",
    values = c("C" = "none", "A" = "none", "I" = "none", "M" = "stripe"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
  scale_fill_manual(
    name = "Treatment",
    values = c("C" = "#555352", "A" = "#FFD045", "I" = "#56C0BC", "M" = "#FFD045", "f" = "black", "m" = "black", "n" = "gray"),
    labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix")
  ) +
 geom_jitter(aes(shape = sex_plots, fill = sex_plots), width = 0.3, height = 0.00, size = 2, color = "white") +
scale_shape_manual(
  name = "Sex",
  values = c("f" = 22, "m" = 21, "n" = 24),
  labels = c("f" = "female", "m" = "male", "n" = "unknown"))+
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 4,
    size = 3,
    color = "#8F8F8F",
    stroke = 2
  ) +  # mean above
  theme_classic(base_size = 10) +
  labs(x = element_blank(), y = "Female total consumption [mm^2]") +
  scale_x_discrete(labels = c("C" = "Control", "A" = "ALAN", "I" = "Insecticide", "M" = "Mix"))+
  theme(
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 20),
    text = element_text(family = "A")
  )+
  ylim(450, 1200)

# Show the plot
food_total_f

# Save the plot
filename <- "food_total_f.svg"
ggsave(filename, plot = food_total_f, device = "svg", width = 6, height = 4)

cat("Plot saved as", filename, "in the working directory.\n")

```

##Fig. S2C_F0 TOTAL CONSUMPTION x LARVAL MASS MALE

```{r}
# Prepare data
all_m_clean <- all_m %>%
  mutate(
    treatment = case_when(
      ALAN == 0 & Cooper == 0 ~ "C",
      ALAN == 1 & Cooper == 0 ~ "A",
      ALAN == 0 & Cooper == 1 ~ "I",
      ALAN == 1 & Cooper == 1 ~ "M",
      TRUE ~ NA_character_
    ),
    treatment = factor(treatment, levels = c("C", "A", "I", "M"))
  ) %>%
  filter(!is.na(mass_l), !is.na(food_total), is.finite(mass_l), is.finite(food_total))

# Plot
RCRm<- ggplot(all_m_clean, aes(x = mass_l, y = food_total,
                        color = treatment, linetype = treatment)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(method = "lm", se = FALSE, linewidth = 1.2) +
  scale_color_manual(
    name = "Treatment",
    values = c(
      "C" = "#555352",  # Control (gray)
      "A" = "#FFD045",  # ALAN (yellow)
      "I" = "#56C0BC",  # Insecticide (blue)
      "M" = "red"   # Mix (yellow)
    ),
    labels = c(
      "C" = "Control",
      "A" = "ALAN",
      "I" = "Insecticide",
      "M" = "Mix"
    )
  ) +
  scale_linetype_manual(
    name = "Treatment",
    values = c(
      "C" = "solid",
      "A" = "solid",
      "I" = "solid",
      "M" = "dashed"
    ),
    labels = c(
      "C" = "Control",
      "A" = "ALAN",
      "I" = "Insecticide",
      "M" = "Mix"
    )
  ) +
  labs(
    x = "Larval mass [mg]",
    y = "Total feeding amount [mm^2]",
    title = "Relationship between early larval mass and RCR"
  ) +
  theme_classic(base_size = 10) +
  theme(
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 20),
    plot.title = element_text(size = 22, hjust = 0.5),
    legend.title = element_text(size = 16),
    legend.text = element_text(size = 14),
    text = element_text(family = "A")
  )+
    ylim(500, 1200)+
  xlim(0.25, 1.75)


RCRm 


# Save the plot
filename <- "RCRm.svg"
ggsave(filename, plot = RCRm, device = "svg", width = 6, height = 4)

cat("Plot saved as", filename, "in the working directory.\n")
```

##Fig. S2D_F0 TOTAL CONSUMPTION x LARVAL MASS FEMALE

```{r}
# Prepare data
all_f_clean <- all_f %>%
  mutate(
    treatment = case_when(
      ALAN == 0 & Cooper == 0 ~ "C",
      ALAN == 1 & Cooper == 0 ~ "A",
      ALAN == 0 & Cooper == 1 ~ "I",
      ALAN == 1 & Cooper == 1 ~ "M",
      TRUE ~ NA_character_
    ),
    treatment = factor(treatment, levels = c("C", "A", "I", "M"))
  ) %>%
  filter(!is.na(mass_l), !is.na(food_total), is.finite(mass_l), is.finite(food_total))

# Plot
RCRf <- ggplot(all_f_clean, aes(x = mass_l, y = food_total,
                        color = treatment, linetype = treatment)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(method = "lm", se = FALSE, linewidth = 1.2) +
  scale_color_manual(
    name = "Treatment",
    values = c(
      "C" = "#555352",  # Control (gray)
      "A" = "#FFD045",  # ALAN (yellow)
      "I" = "#56C0BC",  # Insecticide (blue)
      "M" = "red"   # Mix (yellow)
    ),
    labels = c(
      "C" = "Control",
      "A" = "ALAN",
      "I" = "Insecticide",
      "M" = "Mix"
    )
  ) +
  scale_linetype_manual(
    name = "Treatment",
    values = c(
      "C" = "solid",
      "A" = "solid",
      "I" = "solid",
      "M" = "dashed"
    ),
    labels = c(
      "C" = "Control",
      "A" = "ALAN",
      "I" = "Insecticide",
      "M" = "Mix"
    )
  ) +
  labs(
    x = "Larval mass [mg]",
    y = "Total feeding amount [mm^2]",
    title = "Relationship between early larval mass and RCR"
  ) +
  theme_classic(base_size = 10) +
  theme(
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 20),
    plot.title = element_text(size = 22, hjust = 0.5),
    legend.title = element_text(size = 16),
    legend.text = element_text(size = 14),
    text = element_text(family = "A")
  )+
  ylim(500, 1200)+
  xlim(0.25, 1.75)

RCRf 


# Save the plot
filename <- "RCRf.svg"
ggsave(filename, plot = RCRf, device = "svg", width = 6, height = 4)

cat("Plot saved as", filename, "in the working directory.\n")

```


